Galaxy image statistical generator: how to be confident?

### 2024-09-10 paper/main.tex
experiemnt start

@@

\begin{document}
\maketitle
%\renewcommand{\baselinestretch}{0.75}\normalsize
%\tableofcontents
%\renewcommand{\baselinestretch}{1.0}\normalsize
%
\begin{abstract}
blabla
\\
\smallskip
\noindent \textbf{Keywords.} diffusion models, U-Net
\end{abstract}

@@

Concerning the training dataset, as we need to train two models with up to $100,000$ images each, we have used the SDSS (Sloan Digital Sky Survey) dataset used in \citep{smith2021}\footnoe{See \url{https://github.com/Smith42/astroddpm} to obtain the raw data.} but first all images are cropped about the target coordinate galaxy to a shape of $64\times 64$ pixels and from the $z,g,r$ channels we produce a single  channel in gray levels in the range $[0,1]$ using \texttt{scipy} \citep{2020SciPy-NMeth} library\footnote{In particular the \texttt{make_lupton_rgb} function has been applied with $Q=8$ and $stretch=0.2$ setting}. Moreover, the gray level is coded using 5-bits precision.
{\color{red}The training dataset of $250,000$ galaxies is available in github}. With such dataset,  according to \cite{kadkhodaie2024generalization} results, the transition between memorization to generalisation regimes is expected to occur with size the range $10^4-10^5$.

>>>>

\newenvironment{nouppercase}{%
  \let\uppercase\relax%
  \renewcommand{\uppercasenonmath}[1]{}}{}

@@

\begin{document}
\begin{nouppercase}
\maketitle
\end{nouppercase}
%\renewcommand{\baselinestretch}{0.75}\normalsize
%\tableofcontents
%\renewcommand{\baselinestretch}{1.0}\normalsize
%
\begin{abstract}
blabla
\\
\smallskip
\noindent \textbf{Keywords.} diffusion models, U-Net
\end{abstract}

@@

Concerning the training dataset, as we need to train two models with up to $100,000$ images each, we have used the SDSS (Sloan Digital Sky Survey) dataset used in \citep{smith2021}\footnote{See \url{https://github.com/Smith42/astroddpm} to obtain the raw data.} but first all images are cropped about the target coordinate galaxy to a shape of $64\times 64$ pixels and from the $z,g,r$ channels we produce a single  channel in gray levels in the range $[0,1]$ using \texttt{scipy} \citep{2020SciPy-NMeth} library\footnote{In particular the \texttt{make\_lupton\_rgb} function has been applied with $Q=8$ and $stretch=0.2$ setting}. Moreover, the gray level is coded using 5-bits precision.
{\color{red}The training dataset of $250,000$ galaxies is available in github}. With such dataset,  according to \cite{kadkhodaie2024generalization} results, the transition between memorization to generalisation regimes is expected to occur with size the range $10^4-10^5$.
